
---
title: "Plotly using HTML Widgets in R"
output:
  html_document:
    toc: true
---

#HTML Widgets in Databricks R Notebooks
This example notebook shows how to use libraries like Plotly and other libraries such as Leaflet and Dygraphs. To get setup, the user requires [R HTML widgets](http://www.htmlwidgets.org/) working in Databricks notebooks. This setup has two steps:
1. Installing `pandoc`, a Linux package that is used by HTML widgets to generate HTML
2. Changing one function within HTML Widgets package to make it seemlessly work in Databricks. Make sure you use correct URL of your Databricks environment.

This notebook shows a Plotly example using HTMLWidgets

```{r}
%md
Reference articles: [HTML Widgets in Azure Databricks R Notebooks](https://docs.microsoft.com/en-us/azure/databricks/_static/notebooks/azure/htmlwidgets-azure.html) \
[HTML Widgets in Databricks R Notebooks](https://docs.databricks.com/_static/notebooks/htmlwidgets.html) \
[HTML Widgets](https://www.htmlwidgets.org/)
```


```{bash}
apt-get --yes install pandoc
```

```{r}
%md
The aim of devtools is to make package development easier by providing R functions that simplify and expedite common tasks.
```


```{r}
require(devtools)
install_version("htmltools", version = "0.4.0", repos = "http://cran.us.r-project.org")
```


```{r}
library(htmltools)
```


```{r}
install.packages("htmlwidgets")
```


```{r}
library(htmlwidgets)
```


```{r}

## URL of your Azure Databricks Account
## Replace <region> with the region of your Azure Databricks Account URL
## Make sure you use HTTPS
databricksURL <- "<region>/files/rwidgets/"

```


```{r}
install.packages("R.utils")
```


```{r}
## Fix HTML Widgets package to work in Azure Databricks Notebooks
## Replace <workspace-id> with the workspace ID of your Azure Databricks Account URL
db_html_print <- function(x, ..., view = interactive()) {
  fileName <- paste(tempfile(), ".html", sep="")
  htmlwidgets::saveWidget(x, file = fileName)
  
  randomFileName = paste0(floor(runif(1, 0, 10^12)), ".html")
  baseDir <- "/dbfs/FileStore/rwidgets/"
  dir.create(baseDir)
  internalFile = paste0(baseDir, randomFileName)
  externalFile = paste0(databricksURL, randomFileName, "?o=<workspace-id>")
  system(paste("cp", fileName, internalFile))
  displayHTML(externalFile)
}
R.utils::reassignInPackage("print.htmlwidget", pkgName = "htmlwidgets", value = db_html_print)
```

# Example with `plotly`

```{r}
install.packages("plotly")
```


```{r}
library(plotly)
p <- plot_ly(midwest, x = ~percollege, color = ~state, type = "box")
p
```

